A multinomial spatio-temporal model for sexual risk behaviour in AGYW

### 2022-01-04 docs/09-09-21_three-category/three-category.Rmd
Swaziland is now Eswatini everywhere (I hope) #56

* Estimate proportions indexed by
  * District $i = 1, \ldots, n$
    * 13 AGYW Global Fund priority countries (but fitting individually): Botswana, Cameroon, Kenya, Lesotho, Malawi, Mozambique, Namibia, South Africa, Swaziland, Tanzania, Uganda, Zambia and Zimbabwe
  * Survey $t = 1, \ldots, T$
    * The available DHSs
  * Age $a \in \{\text{15--19}, \text{20--24}, \text{25--29}\}$
  * Category $k$
* e.g. in Lilongwe, in 2015, how many AGYW aged 20-24 are cohabiting with a single partner?

>>>>

* Estimate proportions indexed by
  * District $i = 1, \ldots, n$
    * 13 AGYW Global Fund priority countries (but fitting individually): Botswana, Cameroon, Eswatini, Kenya, Lesotho, Malawi, Mozambique, Namibia, South Africa, Tanzania, Uganda, Zambia and Zimbabwe
  * Survey $t = 1, \ldots, T$
    * The available DHSs
  * Age $a \in \{\text{15--19}, \text{20--24}, \text{25--29}\}$
  * Category $k$
* e.g. in Lilongwe, in 2015, how many AGYW aged 20-24 are cohabiting with a single partner?
